An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-26 0_main.tex
'beading strategy' ==> 'beading scheme'

A simple technique for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a uniform width.
In the center of the outline shapes this simple technique can result in underfill regions and overfill regions as wide as the nozzle size.
Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

@@

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our open source implementation exhibits computation times in the same order of magnitude as the state-of-the-art implementation of the uniform width technique.
\end{abstract}

>>>>

A simple technique for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a uniform width.
In the center of the outline shapes this simple technique can result in underfill regions and overfill regions as wide as the nozzle size.
Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
We propose a framework which allows to define beading schemes which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

@@

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading schemes.
We show that we can define a scheme which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our open source implementation exhibits computation times in the same order of magnitude as the state-of-the-art implementation of the uniform width technique.
\end{abstract}

### 2019-08-26 10_applications.tex
'beading strategy' ==> 'beading scheme'

\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading strategy.
Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources/applications/combined_small_dilated_circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
}
\caption{\censor{TUD}}\label{applications_tud}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
\caption{\censor{UM}}\label{applications_um}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading strategy applied to various example application objects.
A legend for the colors can be found in \cref{visualized_accuracy}.
From left to right and top to bottom: a house, a case for electronics, a statue, two logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

>>>>

\Cref{applications_overview} shows the widths of generated layer toolpaths for various types of 3D model using the inward distributed beading scheme.
Thin parts often occur in architectural models, casings, embossed text, gears and microstructures.
Also in larger regions and organic shapes (\cref{applications_case} and \subref{applications_statue}) our method finds succesful application.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.099\textwidth}
\setlength{\figheight}{0.099\textwidth}
\begin{subfigure}{\textwidth}\centering
\includegraphics[width=\textwidth]{sources/applications/combined_small_dilated_circled.pdf}
%\caption{Overview}\label{applications_overview}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/house.png}
\caption{House}\label{applications_house}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pocket_operator_case.png}
\caption{Case}\label{applications_case}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/david.png}
\caption{Statue}\label{applications_statue}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\censorbox{
\includegraphics[height=\figheight]{sources/applications/tud_logo.png}
}
\caption{\censor{TUD}}\label{applications_tud}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/ultimaker_logo.png}
\caption{\censor{UM}}\label{applications_um}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/pinion_gear_motor.png}
\caption{Gear}\label{applications_gear}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/topopt_bone.png}
\caption{Bone}\label{applications_bone}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/gyroid.png}
\caption{Gyroid}\label{applications_gyroid}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/applications/hex_grid.png}
\caption{Hex}\label{applications_hex}
\end{subfigure}
\caption{
Visualization of the widths for the output toolpaths of the inward distributed beading scheme applied to various example application objects.
A legend for the colors can be found in \cref{visualized_accuracy}.
From left to right and top to bottom: a house, a case for electronics, a statue, two logos, a gear, a topologically optimized bone structure, a homogeneous lateral thickness tilted gyroid structure and a heterogeneous thickness hexagonal grid.
}
\label{applications_overview}
\end{figure*}

### 2019-08-26 12_conclusions_future_work.tex
'beading strategy' ==> 'beading scheme'

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
Our framework is shown to be flexible, since we have shown several beading strategies which emulate existing techniques and the computation times are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
Our framework is robust and local, meaning that small changes in the toolpath are caused by small local changes in the outline shape.

We have introduced the inward distributed beading strategy which reduces the amount of beads with a width deviating from the nominal bead width by a large amount
and instead distributes the deviation in bead width over several beads near the center of the shape.
That way the impact of adaptive bead width on mechanical properties of the resulting print are limited.
Moreover the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realized adaptive bead width.

The proposed beading strategy greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
On the other hand it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.

\subsection{Future work}
The work presented here is evaluated mostly on a theoretical level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the validation of our techniques.
Future research might be devoted to optimizing the distribution scheme to a specific hardware setup.
If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading strategy.

>>>>

\section{Conclusion and future work}
In this paper we have introduced a framework for computing contour parallel toolpaths employing adaptive bead width in order to minimize underfill and overfill areas.
Our framework is shown to be flexible, since we have shown several beading schemes which emulate existing techniques and the computation times are on par with the state-of-the-art library for performing offsets of non-adaptive bead width.
Our framework is robust and local, meaning that small changes in the toolpath are caused by small local changes in the outline shape.

We have introduced the inward distributed beading scheme which reduces the amount of beads with a width deviating from the nominal bead width by a large amount
and instead distributes the deviation in bead width over several beads near the center of the shape.
That way the impact of adaptive bead width on mechanical properties of the resulting print are limited.
Moreover the outer toolpath is affected less by the deviation, meaning that the dimensional accuracy in the horizontal direction is affected less by inaccuracies in the mechanical system which realized adaptive bead width.

The proposed beading scheme greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
On the other hand it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.

\subsection{Future work}
The work presented here is evaluated mostly on a theoretical level, because the effectiveness of a mechanical system to accurately print an adaptive bead width interferes with the validation of our techniques.
Future research might be devoted to optimizing the distribution scheme to a specific hardware setup.
If we can assign a loss function to several aspects (e.g. manufacturability, print speed, dimensional accuracy) of a toolpath we could deduce the optimal beading scheme.

### 2019-08-26 4_method.tex
'beading strategy' ==> 'beading scheme'

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading strategy and we show several such beading strategies.

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on an edge of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

@@

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a quantization operator which maps a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framework the function $q$ is determined by a beading strategy.

@@

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading strategy: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

@@

\subsection{Peripheral heights}\label{sec_peripheral_height_adjustment}
Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e. the periphery, and slice the resulting mesh into isocontour toolpaths.
The peripheral heights could be determined in a plethora of ways according to various beading strategies.
The ramps from the outline shape to the center might have various curves,
but for our example we use straight ramps, just like the original UoC.
See \cref{peripheral_heights}.
That means we can stretch the $R$ heights of the UoC with a multiplier depending on the height of the center in terms of bead count.

@@

After each marked node is assigned a beading by the beading strategy, we propagate the beadings outward to all nodes in the ST.
The beading propagation is performed in two stages: an upward and downward stage.
%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.

>>>>

This section explains how we can generate toolpaths with evenly distributed bead widths.
We describe how to construct the mesh of the UoC in \cref{sec_surface_construction} and
explain how to identify central regions in \cref{sec_center_classification}.
Quantizing and smoothing the heights in the central mesh regions are handled in \cref{sec_central_height_adjustment}.
We then describe how to deal with heights in the periphery in \cref{sec_peripheral_height_adjustment}
and describe the toolpath extraction algorithm in \cref{sec_toolpath_extraction}.
In \cref{sec_generalization} we describe how to generalize our method for generating evenly distributed bead widths into a general framework for generating contour parallel toolpaths using an arbitrary beading scheme and we show several such beading schemes.

@@

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_ovp_1} \leq \si{180}{\degree}$ between a location $v$ on an edge of the ST and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Edges are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading scheme.

@@

%\subsubsection{Initial bead count}\label{sec_initial_bead_count}
In order to update the bead count values, we require a quantization operator which maps a feature diameter to a bead count: $q: \mathbb{R} \to \mathbb{N}$.
For our example we choose to round to the nearest integer multiple of the nozzle size $w_\text{pref}$: $q(d) = \left\lfloor \nicefrac{d}{w_\text{pref}} + \nicefrac12 \right\rfloor$.
In our generalized framework the function $q$ is determined by a beading scheme.

@@

A transition with length $t(n)$ will be placed somewhere covering the transition anchor position.
We require an additional function to be specified by the beading scheme: $t_0(n)$ determines the distance between the lower end of a transition from bead count $n$ to $n+1$ and the anchor point - as measured along the marked edges of the ST.
From that we calculate $t_1(n) = t(n) - t_0(n)$ for the distance from the anchor to the upper end of the transition.
For our example we can simply use $t_0(n) = t_1(n) = \nicefrac12 w_\text{pref}$, so that the transition ramp is centered on the anchor position.

@@

\subsection{Peripheral heights}\label{sec_peripheral_height_adjustment}
Now that we have transformed the heights in the central regions of the UoC we need to determine the heights in the rest of the shape, i.e. the periphery, and slice the resulting mesh into isocontour toolpaths.
The peripheral heights could be determined in a plethora of ways according to various beading schemes.
The ramps from the outline shape to the center might have various curves,
but for our example we use straight ramps, just like the original UoC.
See \cref{peripheral_heights}.
That means we can stretch the $R$ heights of the UoC with a multiplier depending on the height of the center in terms of bead count.

@@

After each marked node is assigned a beading by the beading scheme, we propagate the beadings outward to all nodes in the ST.
The beading propagation is performed in two stages: an upward and downward stage.
%First we sort all upward half-edges on the radial distance of their destination node, so that we can efficiently flood fill the beading information.
In the upward phase we walk from each marked node upward along unmarked edges and map each node encountered to a pair consisting of the traversed distance and the bottom source beading.
In the downward phase we walk from each marked node downward along unmarked edges and map each node to a pair consisting of the traversed distance and the upper source beading -
however, if we encounter a node which was already mapped to an upward propagated beading we employ the interpolation scheme described above in order to define the beading, which is then further propagated downward.
This is implemented in a flood-fill fashion: see \cref{alg_beading_propagation}.

### 2019-08-26 5_generalization.tex
'beading strategy' ==> 'beading scheme'

\section{Generalization}\label{sec_generalization}
In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
Depending on the application, the hardware and the materials used we might need different strategies for determining the bead widths.
In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
There are several strategies one can take for determining the distribution of bead widths.
We will formalize several strategies and describe the set of parameters these strategies require.

\begin{definition}\label{beading_strategy_definition}
We define a beading strategy as the following set:
$$
\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
$$
where
$\alpha_{\text{max}}$ (the limit bisector angle),
$q(d)$ (quantization operator),
$t(n)$ (transition length)
and
$t_0(n)$ (transition anchor position) have already been defined above.
We introduce here
$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
and
$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
\end{definition}

@@

\subsection{Beading strategies}
We introduce several beading strategies which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by defining new beading strategies.
We also introduce new beading strategies which produce toolpaths with less extremal widths compared to techniques from existing literature.

A beading strategy is defined as a set of some particular variables and functions (\cref{beading_strategy_definition}).
Our beading strategies are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading strategies we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( q^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\paragraph{Uniform Beading Strategy}
We can define a beading strategy which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Outer bead}
We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading strategy functions deal with the outermost bead.
Also we turn off the reduction of toolpaths near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading strategy on the bead count $q^-(d)$ defined by the uniform beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

@@

\paragraph{Evenly distributed}
By taking the advantages of the above two strategies we can define a beading strategy which constitutes a novel toolpathing technique.
We can evenly divide the local feature diameter over the widths of all beads, but choose a local bead count better matching the local feature size.
We determine the local bead count by dividing the diameter by the prefered bead width and rounding to the nearest integer.
This reduces the demands on the system and deviation from mechanical properties caused by beads with extreme deviations from the preferred width.

@@

\paragraph{General distributed strategy}
The evenly distributed strategy can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w_\text{pref} + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading strategy which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform strategy will still hold approximately.

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
\setlength{\figheight}{.25\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_inward.png}
\caption{Inward distributed}
\end{subfigure}
\begin{subfigure}{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_legend.png}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading strategies for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}

\paragraph{Widening}
Complementary to any of these strategies we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
We can simply override
\begin{align*}
W'(n,d)_1 &=
\begin{cases}
\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
W(n,d)_1 & \text{ otherwise}
\end{cases}
\end{align*}

>>>>

\section{Generalization}\label{sec_generalization}
In this section we will generalize the described method into a parametric system, i.e. an algorithmic framework.
The method we have described above is one for distributing the beads evenly over the total diameter of an outline shape feature.
Depending on the application, the hardware and the materials used we might need different schemes for determining the bead widths.
In this section we will generalize the method so that we can apply any distribution of bead widths over a feature radius.
There are several schemes one can take for determining the distribution of bead widths.
We will formalize several schemes and describe the set of parameters these schemes require.

\begin{definition}\label{beading_scheme_definition}
We define a beading scheme as the following set:
$$
\left\{ \alpha_\text{max}, q(d), t(n), t_0(n), W(n, d), L(n, d) \right\}
$$
where
$\alpha_{\text{max}}$ (the limit bisector angle),
$q(d)$ (quantization operator),
$t(n)$ (transition length)
and
$t_0(n)$ (transition anchor position) have already been defined above.
We introduce here
$W(n, d)$, which gives the sequence of bead widths $\left\{ w_i \right\}$ for each bead with index $i$
and
$L(n, d)$, which gives the sequence of radial locations $\left\{ l_i \right\}$ which map to each bead index $i$.
\end{definition}

@@

\subsection{Beading schemes}
We introduce several beading schemes which determine the bead count and their widths in various ways.
We can emulate a variety of toolpath generation methods from related literature by defining new beading schemes.
We also introduce new beading schemes which produce toolpaths with less extremal widths compared to techniques from existing literature.

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w_\text{pref} = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter} \\
d^\text{discretization} &= \SI{0.2}{\milli\meter} \\
t_\text{beading} &= w_\text{pref} \\
d_\text{max}^\text{intersection} &= \SI{75}{\percent} \\
%
%We use a transition anchor position of
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - p(n) }{p(n+1) - p(n) }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4(n+1) - 0.4n }$$
%$$t_-(n) =  t(n) \frac{ q^{-1}(n) - 0.4n }{0.4}$$
t_0(n) &=  t(n) \left( q^{-1}(n) / w_\text{pref}  - n \right) \\
t(n) &= w_\text{pref} \\
\alpha_\text{max} &= \SI{135}{\degree} \\
L(n,d)_i &= 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\end{align*}

@@

\paragraph{Uniform Beading scheme}
We can define a beading scheme which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

\paragraph{Outer bead}
We can emulate the method by \citeauthor{Moesen2011} by carefully choosing how the beading scheme functions deal with the outermost bead.
Also we turn off the reduction of toolpaths near 3-way intersections, so that the polygonal toolpaths emulate the remaining area to be filled by another path planning technique similar to their technique.

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading scheme on the bead count $q^-(d)$ defined by the uniform beading scheme.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

@@

\paragraph{Evenly distributed}
By taking the advantages of the above two schemes we can define a beading scheme which constitutes a novel toolpathing technique.
We can evenly divide the local feature diameter over the widths of all beads, but choose a local bead count better matching the local feature size.
We determine the local bead count by dividing the diameter by the prefered bead width and rounding to the nearest integer.
This reduces the demands on the system and deviation from mechanical properties caused by beads with extreme deviations from the preferred width.

@@

\paragraph{General distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w_\text{pref}$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w_\text{pref} + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.

\begin{figure}
\centering
\setlength{\figwidth}{.4\columnwidth}
\setlength{\figheight}{.25\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_evenly.png}
\caption{Evenly distributed}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_inward.png}
\caption{Inward distributed}
\end{subfigure}
\begin{subfigure}{.1\columnwidth}\centering
\includegraphics[height=\figheight]{sources/validation/wedge_Distributed_pretty_legend.png}
\end{subfigure}
\caption{
Closeup of toolpaths generated with the distributed beading schemes for a large wedge shape.
Colors represent bead widths.
}
\label{distributed_comparison}
\end{figure}

\paragraph{Widening}
Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
We can simply override
\begin{align*}
W'(n,d)_1 &=
\begin{cases}
\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
W(n,d)_1 & \text{ otherwise}
\end{cases}
\end{align*}
